A boundary integral equation approach to computing eigenvalues of the Stokes operator

### 2019-04-10 doc/draft-01-stokes/02prelim.tex
minor updates

\section{Mathematical Preliminaries}
\label{sec:prelim}
In this paper, vector-valued
quantities are denoted by bold, lower-case letters
(e.g. $\bh$), while tensor-valued quantities are bold
and upper-case (e.g. $\mathbf{T}$). 
Subscript indices of non-bold characters (e.g. $h_j$ or $T_{ij\ell}$)
are used to denote the entries within a vector ($\bh$) or tensor ($\bT$).
We use the standard Einstein summation convention; in other words, 
there is an implied sum taken over the repeated indices of 
any term (e.g. the symbol $a_{j} b_{j}$ is used to represent the sum
$\sum_{j} a_{j} b_{j}$).
If $\xx = (x_1,x_2)^\intercal$, then $\xx^\bot = (-x_2,x_1)^\intercal$.
Similarly, $\nabla^\bot = (-\partial_{x_2},\partial_{x_1})^\intercal$.
Upper-case script characters (e.g. $\mathcal{K}$) are reserved for
operators on Banach spaces, with $\mathcal{I}$ denoting the
identity. Given a set $X$, we denote the closure of $X$
by $\overline{X}$.

>>>>

\section{Mathematical Preliminaries}
\label{sec:prelim}
In this paper, vector- and tensor-valued quantities
are denoted by bold letters (e.g. $\bh$ and $\mathbf{T}$). 
Subscript indices of non-bold characters (e.g. $h_j$ or $T_{ij\ell}$)
are used to denote the entries within a vector or tensor.
We use the standard Einstein summation convention; i.e., 
there is an implied sum taken over the repeated indices of 
any term (e.g. the symbol $a_{j} b_{j}$ is used to represent the sum
$\sum_{j} a_{j} b_{j}$).
If $\xx = (x_1,x_2)^\intercal$, then $\xx^\bot = (-x_2,x_1)^\intercal$.
Similarly, $\nabla^\bot = (-\partial_{x_2},\partial_{x_1})^\intercal$.
Upper-case script characters (e.g. $\mathcal{K}$) are reserved for
operators on Banach spaces, with $\mathcal{I}$ denoting the
identity. Given a set $X$, we denote the closure of $X$
by $\overline{X}$.
